PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in OCIR RAMP data

## RAMP
```{r coping ramp ocir cols}
if(RAMP == TRUE) {
coping.ramp.ocir.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ocir_coping_ramp.rds"))
dim(coping.ramp.ocir.raw)
colnames(coping.ramp.ocir.raw)
}
```

```{r coping ramp ocir summary labels}
if(RAMP == TRUE) {
summarytools::dfSummary(
  coping.ramp.ocir.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
}
```

*Note that the COPING RAMP OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
```{r coping ramp ocir cleaning}
if(RAMP == TRUE) {
coping.ramp.ocir.raw.id <- coping.ramp.ocir.raw %>%
    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from RAMP prepandemic
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from RAMP prepandemic
    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from RAMP prepandemic
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from RAMP prepandemic
    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from RAMP prepandemic
    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from RAMP prepandemic
    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from RAMP prepandemic
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from RAMP prepandemic
    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from RAMP prepandemic
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from RAMP prepandemic
    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from RAMP prepandemic
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from RAMP prepandemic
    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from RAMP prepandemic
    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from RAMP prepandemic
    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from RAMP prepandemic

# Inspect dimensions
dim(coping.ramp.ocir.raw.id)
# Inspect colnames
colnames(coping.ramp.ocir.raw.id)
#Differences
dim(coping.ramp.ocir.raw)[1]-dim(coping.ramp.ocir.raw.id)[1]
}
```

>>>>

## RAMP
```{r coping ramp ocir cols}
if(RAMP == TRUE) {
ramp.ocir.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ocir_ramp.rds"))
dim(ramp.ocir.raw)
colnames(ramp.ocir.raw)
}
```

```{r coping ramp ocir summary labels}
if(RAMP == TRUE) {
summarytools::dfSummary(
  ramp.ocir.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
}
```

*Note that the COPING RAMP OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
```{r coping ramp ocir cleaning}
if(RAMP == TRUE) {
ramp.ocir.raw.id <- ramp.ocir.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    ocir.felt_pandemic_feelings = ocir.feelings_pandemic_felt, # Comparison to before the pandemic
    ocir.saved_things_retro = ocir.saved_things.1,
    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary..1,
    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset.1,
    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel.1, 
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply.1, 
    ocir.mind_upset_unpleasant_thoughts_retro = ocir.unpleasant_thoughts_mind_upset.1,
    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things.1,
    ocir.light_switches_water_taps_retro = ocir.repeatedly_check_gas_water.1,
    ocir.arranged_things_retro = ocir.arranged_things.1,
    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel.1, 
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash.1, 
    ocir.frequently_difficulty_rid_nasty_retro = ocir.difficulty_rid_frequently_nasty.1,

    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, 
    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, 
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., 
    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from RAMP prepandemic
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from RAMP prepandemic
    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
    ocir.arranged_things_base = ocir.arranged_things.1,
    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from RAMP prepandemic
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from RAMP prepandemic
    ocir.saved_things_base = ocir.saved_things.1,
    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from RAMP prepandemic
    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from RAMP prepandemic
    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from RAMP prepandemic
    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(ramp.ocir.raw.id)
# Inspect colnames
colnames(ramp.ocir.raw.id)
#Differences
dim(ramp.ocir.raw)[1]-dim(ramp.ocir.raw.id)[1]
}
```
